Hypertension and microbiome

### 2019-06-07 articletwo.Rmd
Run maaslin on R 3.4.3 by rscript

```{r fit asine}
source("fit_asine.R")
source("taxa_names_functions.R")

if (!file.exists("rds/maaslin.rds")) {
    pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
    pseq.genus.core.comp <- microbiome::transform(pseq.genus.core, "compositional")

    res <- lapply(c2l(var.BP), function(BP)
        fit_asine(pseq.genus.core.comp, variables = c(BP, var.CL)))

    res.trim <- lapply(c2l(var.BP), function(BP)
        lapply(c2l(names(res[[BP]])), function(name) res[[BP]][[name]] %>%
                                                     tidy %>%
                                                     dplyr::filter(grepl(BP, term)) %>%
                                                     mutate(taxa = name)))

    maaslin <- map_df(res.trim, ~do.call(rbind, .x)) %>%
        dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
        arrange(Qval)

    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```

```{r quit}
quit()
```

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        tibble::rownames_to_column("ids") %>%
        tibble::column_to_rownames("ids") %>%
        select(var.BP, var.CL)

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame

    maaslin <- Maaslin2(maaslin.abund %>% select(g_Sutterella, g_Adlercreutzia, g_Anaerotruncus),
                        maaslin.pheno,
                        "maaslin2_example_output",
                        transform = "AST",
                        normalization = "NONE",
                        fixed_effects = paste0(var.CL, collapse = ","),
                        random_effects = paste0(var.BP, collapse = ","))

    random_formula = as.formula("expr ~ (1 | MAP) + (1 | SYSTM) + (1 | DIASM) + (1 | PULSEPRESSURE) + (1 | HYPERTENSION)")
    formula = as.formula("expr ~  BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09")

    formula2 <-
                    paste(
                        '. ~', 
                        paste(all.vars(formula)[-1], collapse = ' + '), 
                        '.', 
                        sep = ' + ')

    formula2

    update(random_formula, formula2)

    maaslin.pheno %>% head(n=1)

    stats::glm(BL_AGE ~ SEX + (1|MAP), family = stats::gaussian, data = meta(pseq.genus.core))

    maaslin$results %>% head(n=1)

    maaslin.abund[1:10,1:10]
    maaslin.pheno[1:10,1:10]

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
             normalization = "NONE",
             random_effects = paste0(var.BP, collapse = ","),
             fixed_effects = paste0(var.CL[1:3], collapse = ","), 
             cores = detectCores())

    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```

>>>>

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
    pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
    pseq.genus.core.viruses <- taxa(pseq.genus.core.comp) %>% mygrep(word = "virus$", complement = TRUE)
    pseq.genus.core.pruned <- prune_taxa(pseq.genus.core.viruses, pseq.genus.core.comp)

    maaslin <- maaslinwrapper(pseq = pseq.genus.core.pruned,
                                    looped = var.BP,
                                    forced = var.CL,
                              taxa = taxa(pseq.genus.core.pruned))

    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS(file = "rds/maaslin.rds")
}
